% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\addtolength{\textheight}{1in}
\addtolength{\textwidth}{.5in}
\addtolength{\voffset }{-.5in}
\addtolength{\oddsidemargin }{-.5in}
\setlength{\parindent}{0pt}

\renewcommand\familydefault{\sfdefault}
\renewcommand\labelitemi{--}

\begin{document}

\name{{\LARGE Kyle W. Rader}}
\address{425.241.7977 $|$ kyle@kylerader.ninja $|$ https://kylerader.ninja $|$ github.com/kyle-rader}

\begin{resume}

\section{EDUCATION}
    {\bf Western Washington University}, Bellingham, WA \\
    {\sl M.S.} Computer Science, 3.89 GPA {\small Finishing research on the side, graduating spring 2018 } \\
    {\sl B.S.} Computer Science, {\small June 2014} Minors: Mathematics, Embedded Systems Engineering

\section{WORK EXPERIENCE}

	%-- ActionSprout --%
    {\bf Software Engineer} -- ActionSprout -- {\sl Do good with Facebook } \\
    {\footnotesize Redmond/Bellingham, WA $|$ https://actionsprout.com $|$ July 2016 - March 2018 }
    \begin{itemize} \itemsep -1pt
        \item Organized a software development team by formalizing code documentation,
            git and BitBucket usage, and project management tools.
        \item In the span of four months moved the company from a scattered product idea to the first launch of an augmented reality runtime engine codename "Catapult".
        \item Develop software architecture for augmented reality runtime systems and applications.
        \item Manage live demos for potential customers and pitch to investors.
        \item Travelled to China for three months during an aqui-hire of the company to help integrate four international software teams.
    \end{itemize}

    %-- 8las --%
    {\bf Software Development Life Cycle Manager} -- 8las/Realmax -- {\sl Augmented Reality } \\
    {\footnotesize Bellingham, WA $|$ http://www.realmax.com/ $|$ July 2015 - July 2016}
    \begin{itemize} \itemsep -1pt
        \item Organized a software development team by formalizing code documentation,
            git and BitBucket usage, and project management tools.
        \item In the span of four months moved the company from a scattered product idea to the first launch of an augmented reality runtime engine codename "Catapult".
        \item Develop software architecture for augmented reality runtime systems and applications.
        \item Manage live demos for potential customers and pitch to investors.
        \item Travelled to China for three months during an aqui-hire of the company to help integrate four international software teams.
    \end{itemize}

    %-- Womp Mobile --%
    {\bf Production Engineer} -- {\sl Womp Mobile} \\
    {\footnotesize Bellingham, WA $|$ https://wompmobile.com $|$ March 2015 - August 2015}
    \begin{itemize} \itemsep -1pt
        \item Mobilized desktop websites using HTML, SASS, \& JavaScript with WompMobile's proprietary internal mobile site builder.
    \end{itemize}

    %-- Uzility --%
    {\bf Director of Engineering} -- {\sl Uzility} \\
    {\footnotesize Bellingham, WA $|$ https://uzility.com $|$ December 2013 - November 2014} \\
    Uzility was a start-up company building an agile software management solution.
    \begin{itemize}  \itemsep -1pt
        \item Developed a web-based Kanban system for agile software development.
        \item Practiced agile software development and lean start-up methodology.
        \item Front and work in HTML, JavaScript, CSS/LESS. Back end work in PHP and MySQL.
    \end{itemize}

    %-- Software Engineer --%
    {\bf Software Engineer} -- {\sl Brer Technical Inc.} \\
    {\footnotesize Bellingham, WA $|$ http://brertechnical.com $|$ Spring 2012 - Spring 2014}
    \begin{itemize} \itemsep -1pt
        \item Principal architect for a business management system centered on the MFI test procedure.
        \item Designed and built a testing interface for real time data collection and visualization.
        \item Gained an understanding of Windows development, SQLite databases, serial communication, \& concurrency.
    \end{itemize}

    %-- Devops Web Developer --%
    {\bf Devops Engineer} -- {\sl Logos Research Systems} \\
    {\footnotesize Bellingham, WA $|$ https://logos.com $|$ June 2013 - January 2014}
    \begin{itemize} \itemsep -1pt
        \item Developed and maintained an internal Ruby on Rails site housing database and server management tools.
        \item Tools included RabbitMQ message replay, MySQL cluster dashboard, server patch dashboard and MySQL schema migration dashboard.
    \end{itemize}

    %-- Grad teaching Assistant --%
    {\bf Graduate \& Undergraduate Teaching Assistant} -- {\sl Western Washington University} \\
    {\footnotesize Bellingham, WA $|$ https://cse.wwu.edu/computer-science $|$ September 2011 - March 2015}
    \begin{itemize} \itemsep -1pt
      \item Run interactive lab trainings, write grading scripts, manage office hours and often help redfine content.
    \end{itemize}

    %-- Research Assistant --%
    {\bf Research Assistant} -- {\sl Western Washington University} \\
    {\footnotesize Bellingham, WA $|$ http://geometrictomography.com $|$ August 2011 - June 2013}
    \begin{itemize}  \itemsep -1pt
        \item Data processing, GUI design and algorithm implementation in Matlab.
    \end{itemize}

%       {\sl Stunt Actor} \hfill Summer 2010 \\
%       Wing-It Productions, Seattle, Wa
%       \begin{itemize}
%           \item Live audience performances
%       \end{itemize}

%       {\sl Taekwondo Instructor} \hfill Sept 2005 - Sept 2007 \\
%       Hwangs Taekwondo, Redmond, Wa
%       \begin{itemize}
%           \item Instructor of the year 2007.
%       \end{itemize}

\newpage

\section{SIDE PROJECTS}
    {\bf The Puzzle Hunt} \\
    {\footnotesize Bellingham, WA $|$ greatpuzzlehunt.com $|$ github.com/kyle-rader/greatpuzzlehunt $|$ July 2015 - Present} \\
    The Great Puzzle Hunt is a puzzle game for teams with diverse skillsets to solve amazing puzzles.
    I've developed a real time web application to run this game/event. The web application facilitates registration, team building, and gameplay.
    By allowing players and volunteers to log in and use QR codes to start timers, every team's puzzle solving is timed and scored live.

    {\bf My Meteor Blog} \\
    {\footnotesize https://kylerader.ninja} \\
    This is a MeteorJS website I maintain to play with React and Meteor.  By far the most useful thing on it
    is the time tools (kylerader.ninja/timetools) page for quickly manipulating and copying date strings and unix timestamps for use while
    writing tests about time.

    {\bf Out In Science} \\
    {\footnotesize Bellingham, WA $|$ facebook.com/outinscience $|$ April 2015 - Present} \\
    Out in Science is a group I started at WWU devoted to the promotion and inclusion of LGBTQ+ members of the College of Science and Engineering.
    The group struck a chord and sprang to life and has only grown since.  We put on social events, mixers, and talks.

    {\bf Computer Science Tutoring} \\
    {\footnotesize Bellingham, WA} \\
    During my last 5 years at WWU I continually offered private computer science tutoring to new and former students. References provided upon request.

    {\bf CodeLily $|$ A Code School for Bellingham} \\
    {\footnotesize Bellingham, WA $|$ Sept 2014 - Sept 2015} \\
    CodeLily is an idea for a Code School in Bellingham, WA.  Our team competed in Bellingham Startup Challenge 2014, after which, we decided to spend a year learning about entreprenuship and how we could make CodeLily a reality.  We pitched CodeLily, winning Crowd Favorite, at Bellingham Pitchfest 2015.  CodeLily is currently on hold as the team completes our masters degrees.

    {\bf Learn ELA} \\
    {\footnotesize http://learnela.com} \\
    This is an AngularJS web application I built for an ESL  (English as a second language) teacher and her business.

\section{AWARDS}
    \begin{itemize} \itemsep -3pt
        \item WWU Computer Science Citizenship Award, 2014
        \item Technology Alliance Group: Technology Leader of Tomorrow, 2013
        \item WWU Computer Science Citizenship Scholarship, 2013
        \item Logos Bible Software Scholarship, 2012
        \item Dealer Information Systems Scholarship, 2011
    \end{itemize}

\section{ACTIVITIES}
    \begin{itemize} \itemsep -3pt
    \item Events Committee Member: Technology Alliance Group {\footnotesize (Fall 2015 - Winter 2016)}
    \item Director of Activities WWU ACM {\footnotesize (Fall 2014 - Spring 2015)}
    \item Activities Coordinator WWU ACM {\footnotesize (Spring 2013 - June 2014)}
    \item CCDC/Cyber Defense Club {\footnotesize (Fall 2012 - Spring 2013)}
    \item Jr. Supervisor Bellingham A.I. and Robotics Society. {\footnotesize (Winter 2011 - Winter 2013)}
    \item WWU ACM mentor. {\footnotesize (Spring 2013)}
    \item President: Western Student Robotics Club {\footnotesize(Fall 2010 - Spring 2012)}
    \item Vice President: Institute of Electrical and Electronics Engineers WWU Chapter {\footnotesize(Fall 2011 - Spring 2012)}
    %\item Academic Representative: Associated Students Inter Club Council {\footnotesize (Fall 2010 - Spring 2011)}
    \end{itemize}

\end{resume}

\end{document}
